---
title: "lag_report"
output: html_document
date: "2025-08-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install packages, include=FALSE}
source("utils/setup_packages.R")
install_packages_from_file()
```

```{r source util functions, include=FALSE}
source("utils/load_data.R")
source("LagAnalysis/lag_utils.R")
source("LagAnalysis/lag_functions.R")
source("LagAnalysis/stationarity_cointegration.R")
```

```{r libraries, include=FALSE}
library("tidyverse")
library("tsibble")
library("ggplot2")
library("scales")
library("ggh4x")
```

## Research Question

We examine the lead/lag structure of the individual indices relative to the main 
index in more detail. In doing so, we analyze the relationships between the 
indices both in general and specifically around turning points. The aim is to 
provide a comprehensive overview and to identify starting points for further 
research projects. In particular, we focus on identifying a subset of indices 
that explain the development of the main index especially well in advance.


## Correlation Analysis

### Data Basis for Correlation Analysis

The monthly data was analyzed in two seperate approaches:

- Full window based on data from **1991-01-01** to **2025-02-01**
- Rolling window with a **10 year window frame** and a **1 month step size**, 
starting in 2000 with first complete 10 year window

For each Dataset we extract the correlation for each lag as well as the peak 
correlation across a lag of +/-6 months. The window of +/-6 months was specified
in discussion with the project partners to allow for a qualitative and causal 
interpretation. 

They choice for the rolling window size was mainly motivated by:finding a balance 
between:

- small enough window seize to detect changes over time, 
- large enough seize to not be heavily influence by trends (stationary)
- keep the computational demand within reasonable limits.


```{r Data Import, message=FALSE}
# Full Analysis Data
ccf_tbl_full <- read_csv("LagAnalysis/results/ccf_results_full.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = correlation)
ccf_tbl_full_peak <- read_csv("LagAnalysis/results/ccf_results_full_peak.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = peak_corr)
dcor_tbl_full <- read_csv("LagAnalysis/results/dcor_results_full.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = dcor)
dcor_tbl_full_peak <- read_csv("LagAnalysis/results/dcor_results_full_peak.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = peak_corr)
adf_tbl_full <- read_csv("LagAnalysis/results/adf_results_full.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3))

# Rolling Window Analysis Data
ccf_tbl_roll <- read_csv("LagAnalysis/results/ccf_results_roll.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = correlation)
ccf_tbl_roll_peak <- read_csv("LagAnalysis/results/ccf_results_roll_peak.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = peak_corr)
dcor_tbl_roll <- read_csv("LagAnalysis/results/dcor_results_roll.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = dcor)
dcor_tbl_roll_peak <- read_csv("LagAnalysis/results/dcor_results_roll_peak.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>% 
  rename(corr = peak_dcor)
adf_tbl_roll <- read_csv("LagAnalysis/results/adf_results_roll.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3))
```


### Methods for the Analysis of Correlation Structure

#### Lag Aggregation

- For several different parts of the analysis aggregation over las necessary
- The choice of these aggregation logics is motivated by practical point of view
- Multiple forms of aggregation:
  - Peak Correlation over lags -6 to +6 months: stable measure for correlation
  that is not depended on lag window size
  - Mean Correlation over lags -6 to +6 months: smoother, more robust measure of 
  overall correlation structure that also captures distribution across lags
  - Mean Correlation over lags -6 to -1 months: measure for general predictive
  correlation with more focus on short term predictability
  - Mean Correlation over lags -6 to -4 months: measure for longterm predictive
  correlation


#### Dcor vs CCF

To validate the findings the correlation between the individual time series and
the main index (*C0000000 - KLD*) was analyzed with two different approaches:

- Cross Correlation using **stats::ccf**
- Distance Correlation using **energy::dcor**

The distance correlation can be seen as an upper bound for the cross correlation 
function that measures the linear dependence between the different time series. 
For our analysis the main benefit of the distance correlation is the ability to 
verify our Cross Correlation Results as well as having a "un-directed" correlation
measure. 


#### Industry Aggregation

**Hierarchical Aggreagtion:**
- The hierarchical tree structure in the data creates an inherent imbalance when 
aggregating industry codes across sectors (2-digit codes).
- This imbalance arises from the different levels of granularity in how industry
codes are aggregated.
- Sectors with higher granularity have a deeper tree structure, resulting in 
more leaf nodes.
- Smaller sectors have shallower trees with fewer leaf nodes.

Plot: Amount of unique industry codes per sector -> showing imbalances between 
the different sector: 
```{r Industries per Sector, warning=FALSE}
ccf_tbl_full %>%
  filter(level > 0,
         difference == 0) %>%
  distinct(industry_code, sector, level) %>%
  ggplot(aes(x = sector, fill = factor(level))) +
  geom_bar(position = "stack") +
  theme_minimal() +
  labs(
    title = "Number of Industry Codes by Level",
    x = "Sector",
    y = "Count",
    fill = "Level"
  )
```

- Challenge for our Analysis since indirectly biases/weights the sectors based on 
amount of industry codes
- In the correlation analysis, an implicit weighting bias occurs due to 
sector granularity.
- Sectors with higher granularity contribute more because multiple industry codes 
from those sectors are included if they show good correlation.
- Sectors with lower granularity contribute less, even if their correlation is 
good, since they have fewer industry codes.
- This imbalance limits the contribution of low-granularity sectors.
- To correct for this, correlations will be averaged over sectors when comparing 
different questions to the main index.

Formula to calculate balanced mean/median:
```{r Balanced mean/median, message=FALSE}
# Median
compute_balanced_median <- function(df){
  df %>%
  summarise(sector_median = median(corr, na.rm = TRUE), 
            .by = c(lag, indicator, sector)) %>%
  summarise(median_corr  = mean(sector_median,  na.rm = TRUE), 
            .by = c(lag, indicator))
}

# Mean
compute_balanced_median <- function(df){
  df %>%
  summarise(sector_mean = mean(corr, na.rm = TRUE), 
            .by = c(lag, indicator, sector)) %>%
  summarise(mean_corr  = mean(sector_mean,  na.rm = TRUE), 
            .by = c(lag, indicator))
}
```


**Level Restriction**
Plot Industrie codes per Level
```{r Industries per Level}
ccf_tbl_full %>%
  filter(level > 0,
         difference == 0) %>%
  distinct(industry_code, level) %>%
  ggplot(aes(x = level, fill = factor(level))) +
  geom_bar(position = "stack") +
  theme_minimal() +
  labs(
    title = "Number of Industry Codes by Level",
    x = "Sector",
    y = "Count",
    fill = "Level"
  )
```

- Few Industries in levels 4 and 5
- Only Industries from few sectors
- Analysis should be split between Level 1-3 and 4-5 

#### Residual Scoring
- Goal: Develop Score that allows to compare correlation of different industries
between questions and time windows
- Challenge is that some questions and time windows are less correlated across
all indices
- Score should give information about relative correlation across all questions
and time windows -> allow ranking
- Main Problem with conventional ranking is that it doesn't take into account 
the jumps in correlation between ranks

- Proposed score based on residual of (peak) correlation to industry code with 
highest (peak) correlation  in each question + window
- Square residual to work for both distance correlation and normal correlation
- For each Industry code mean squared residual across all questions and windows
- Squared Residual and mean across questions and windows both penalize outliers
thereby creating a robust ranking that covers all observations 

### Full Window Analysis

**General Overview**
Plot: CCF and Dcor
```{r CCF and DCor, echo=FALSE, warning=FALSE}
# Filter ccf Results
heatmap_data <- ccf_tbl_full %>%
  filter(difference==0,
         level > 0) %>%
  compute_balanced_median

# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(median_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot ccf Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(x = lag, y = indicator, fill = median_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Average Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")


# Dcor Overview
heatmap_data <- dcor_tbl_full %>%
  filter(difference==0,
         level > 0) %>%
  group_by(lag, indicator) %>%
  summarise(median_corr = median(corr, na.rm = TRUE), .groups = "drop")


# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(median_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot dcor Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(x = lag, y = indicator, fill = median_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Average Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")
```
- 
- CCF and the Dcor analysis show similar picture of correlation 

**Correlation Distribution by Question**
Plot: Correlation Distribution by Question
```{r Distribution by Indicator, warning=FALSE, echo=FALSE}
dcor_tbl_full %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         lag %in% c(-6:-1)) %>%
  group_by(indicator, industry_code, sector) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>% 
  # group_by(sector, indicator) %>%
  # summarise(mean_corr = mean(mean_corr), .groups = "drop") %>%
  ggplot(aes(x = indicator, y = mean_corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Average Distance Correlation distribution by Question",
    x = "Indicator (Question)",
    y = "Correlation"
  )

dcor_tbl_full_peak %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         peak_lag %in% c(-6:6)) %>%
  ggplot(aes(x = indicator, y = corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Peak Distance Correlation distribution by Question",
    x = "Indicator (Question)",
    y = "Correlation"
  )
```

**Correlation Distribution by Sectors**

**Correlation Distribution by Levels**
Plot: Distribution over Levels
```{r Distribution over Level, warning=FALSE, echo=FALSE}
dcor_tbl_full %>% 
  filter(level > 0, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(level, industry_code) %>%
  summarise(mean_corr = mean(dcor, na.rm = TRUE), .groups = "drop") %>% 
  ggplot(aes(x = factor(level), y = mean_corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Average Distance Correlation distribution by Level",
    x = "Level",
    y = "Correlation"
  )


dcor_tbl_full_peak %>% 
  filter(level > 0, 
         difference == 0) %>%
  group_by(level, sector) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(x = factor(level), y = mean_corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Average Distance Correlation distribution by Level",
    x = "Level",
    y = "Correlation"
  )
  
```
- Interesting Distribution for Level 4 and 5
- High Median Correlation Suggests that they might be a valid subset for fast
predictions/analysis, since based on fewer industry codes
- further qualitative analysis might be interesting

### Development over time

**General Overview**
Plot:  CCF Rolling Window
```{r CCF Rolling Window}
# Filter ccf Results
heatmap_data <- ccf_tbl_roll %>%
  filter(difference==0,
         level %in% c(1:3)) %>% 
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(correlation, na.rm = TRUE), .groups = "drop")

# Plot ccf Results
ggplot(heatmap_data, aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Average Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")
```

- Plot doesnt allow for qualitative analysis but already hints at certain patterns
- 

```{r CCF Rolling Window + Peak}
# Filter ccf Results
heatmap_data <- ccf_tbl_roll %>%
  filter(difference==0,
         level %in% c(1:3),
         lag %in% c(-6:6)) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(correlation, na.rm = TRUE), .groups = "drop")

# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator, date_window_end) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot ccf Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Average Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")
```

- KLD Series Peak Correlation stays the same over time, 
- Other questions show at least small changes in the lag of the Peak Correlation 
over time. 


**Correlation Distribution by Question**

```{r Distribiton by Indicator, warning=FALSE, echo=FALSE}
dcor_tbl_roll %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(dcor, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Development of Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )

dcor_tbl_roll_peak %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         peak_lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(peak_dcor, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Development of Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```

- Based on the quantile bands a subset of industry codes with higher correlation 
across all questions and the time domain very likely

**Correlation Distribution by Sectors**

**Correlation Distribution by Levels**




### Consitency of Correlation Structure 

- Detect variability within Data by analyzing consistency of ranking.
- Analyze the ranking of indices by correlation and its stability across 
indicators, levels and time
- Stability is quantified using the Jaccard consensus of the top-k ranked 
industry codes.

**Full Window Analysis**
Plot: Consensus and Overlap for Full Window Analysis
```{r Consensus and Overlap (Full), warning=FALSE, echo=FALSE}
# Extract Ranking for our dcor values
dcor_tbl_full_rank <- dcor_tbl_full_peak %>%
  filter(level %in% c(1:3),
         difference == 0) %>%
  group_by(indicator) %>%
  mutate(rank = rank(-corr, ties.method = "min")) %>%
  arrange(indicator, rank) %>%
  ungroup()

k_vec <- c(1, seq.int(10,130,10))

# Calculate Jaccard Consenus between Indicators
jac_curve <- dcor_tbl_full_rank %>%
  compute_topk_jaccard(k_vec) %>%
  rename(value = mean_jacc) %>%
  mutate(metric = "Mean Jaccard")

# Calculate overlap between Indicatos
overlap_curve <- dcor_tbl_full_rank %>%
  compute_topk_overlap(k_vec) %>%
  rename(value = overlap) %>%
  mutate(metric = "Union size")

plot_data <- jac_curve %>%
  bind_rows(overlap_curve)

ggplot(plot_data, aes(x = k, y = value, color = metric)) +
  geom_line() +
  geom_point() +
  facet_wrap(~metric, scales = "free_y") +
  theme_minimal() +
  labs(title = "Consensus & Overlap across top-k sets",
       x = "k (top industries)",
       y = NULL)
```

- Size of the union grows fast in the beginning and after *k = 50*
- For *k < 30* the consensus drops fast -> indicates that the composition of 
the rankings start to differ quite drastically at least for some indicator pairs 
- For *k* betwenn 30 and 50 we achieve a decent consensus, while still keeping 
a relatively small union size. 
- *k = 30* gives small enough set size to detect changes, but still bigh enough 
to not be dominated by noise


```{r Top 30 Distrution by Indicator, echo=FALSE}
# Top 30 ranked Industry Codes per question
top30 <- dcor_tbl_full_rank %>%
  filter(rank <= 30) %>%
  pull(industry_code) %>%
  unique()

# Top 30
dcor_tbl_full_peak %>% 
  filter(difference == 0,
         peak_lag %in% c(-6:6),
         industry_code %in% top30) %>%
  ggplot(aes(x = indicator, y = corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Top 30 - Peak Distance Correlation distribution by Question",
    x = "Indicator (Question)",
    y = "Correlation"
  )
```

**Rolling Window Analysis**
Plot: Consensus and Overlap by Indicator
```{r Consensus and Overlap (Roll), warning=FALSE, echo=FALSE}
# Extract Ranking for our dcor values
dcor_tbl_roll_rank <- dcor_tbl_roll_peak %>%
  filter(level %in% c(1:3),
         difference == 0) %>%
  group_by(indicator, window_id) %>%
  mutate(rank = rank(-corr, ties.method = "min")) %>%
  arrange(indicator, window_id, rank) %>%
  ungroup()

k_vec <- c(1,seq.int(10,130,10))

# Calculate Jaccard Consenus between Windows
jac_curve <- dcor_tbl_roll_rank %>%
  group_by(indicator) %>%
  group_modify(~ compute_topk_jaccard_win(.x, k_vec)) %>%
  rename(value = mean_jacc) %>%
  mutate(metric = "Mean Jaccard")

# Calculate overlap between Indicatos
overlap_curve <- dcor_tbl_roll_rank %>%
  group_by(indicator) %>%
  group_modify(~ compute_topk_overlap(.x, k_vec)) %>%
  rename(value = overlap) %>%
  mutate(metric = "Union size")

plot_data <- jac_curve %>%
  bind_rows(overlap_curve)

# Plots
plot_data %>%
  filter(metric=="Mean Jaccard") %>%
  ggplot(aes(x = k, y = value)) +
  geom_line(color = "#F8766D") +
  geom_point(color = "#F8766D") +
  geom_point(
    data = . %>% filter(k == 30),  # only keep k = 30
    aes(x = k, y = value),
    color = "red", size = 2
  ) +
  facet_wrap(~indicator) +
  theme_minimal() +
  labs(title = "Consensus across top-k sets per Indicator",
       x = "k (top industries)",
       y = NULL)

plot_data %>%
  filter(metric=="Union size") %>%
  ggplot(aes(x = k, y = value)) +
  geom_line(color = "#00BFC4") +
  geom_point(colour = "#00BFC4") +
  geom_point(
    data = . %>% filter(k == 30),  # only keep k = 30
    aes(x = k, y = value),
    color = "red", size = 2
  ) +
  facet_wrap(~indicator) +
  theme_minimal() +
  labs(title = "Overlap across top-k sets per Indicator",
       x = "k (top industries)",
       y = NULL)


```

- For Rolling Analysis *k* = 30 is still a viable cutoff point
- For some questions *k* = 1 is very good -> same top industry code in many 
time windows

Plot: Concensus and Overlap over time window for k=30
```{r Consensus and Overlap by Window, warning=FALSE, echo=FALSE}
k_vec <- 30

# Calculate Jaccard Consenus between Windows
jac_curve <- dcor_tbl_roll_rank %>%
  group_by(date_window_end) %>%
  group_modify(~ compute_topk_jaccard(.x, k_vec)) %>%
  rename(value = mean_jacc) %>%
  mutate(metric = "Mean Jaccard")

# Calculate overlap between Indicatos
overlap_curve <- dcor_tbl_roll_rank %>%
  group_by(date_window_end) %>%
  group_modify(~ compute_topk_overlap(.x, k_vec)) %>%
  rename(value = overlap) %>%
  mutate(metric = "Union size")

plot_data <- jac_curve %>%
  bind_rows(overlap_curve)

ggplot(plot_data, aes(x = date_window_end, y = value, color = metric)) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_wrap(~metric, scales = "free_y") +
  theme_minimal() +
  labs(title = "Consensus & Overlap across top-k sets",
       x = "k (top industries)",
       y = NULL)
```

- ....

**Set Size of Top k Industry Codes**
- Question: "Can Ranking be used to construct suitable predictive sets?"
Plot: Overall set size for differnt k Values
```{r}
# Top 30 ranked Industry Codes per question
k_vec <- c(1,seq.int(10,130,10))

uniq_by_k <- map_dfr(k_vec, ~
  dcor_tbl_roll_rank %>%
    filter(rank <= .x) %>%
    summarise(k = .x,
              n_unique_industries = n_distinct(industry_code))
)

# Plot
uniq_by_k %>%
  ggplot(aes(x = k, y = n_unique_industries)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "k (rank cutoff)", y = "Distinct industry codes")
```

- Figure shows that almost all industry codes are in the top 10 for some question 
and time window at least once
- When using Top k industry codes based on question and time window the overall 
set size quickly becomes too much to be a small subset

- 
- ...



================================================================================
ToDo:

```{r}

top30_ind <- top30 %>% 
  group_by(industry_code) %>% 
  count() %>% 
  filter(n >= 10)
top30_intersect <- top30 %>% 
  filter(industry_code %in% top30_ind$industry_code) %>% 
  group_by(indicator) %>% 
  count()
  
```


```{r}
peak_dcor <- dcor_tbl_roll_peak %>%
  filter(level %in% c(1:3)) %>%
  group_by(indicator, date_window_end) %>%
  slice_max(corr, n = 1, with_ties = FALSE) %>%
  select(indicator, date_window_end, corr) %>%
  rename(peak_corr = corr)


```

### Identify interesting Subsets

Over all Questions (Peak thing)
- Set highly correlated
- Set low correlated
- Set high variance


Best Predictor (-6:-1)
- Set best predictor 


Best early predictor (-6:-4)
- Set best predictor 

By BB Tunring Points
- 