---
title: "lag_report"
output: html_document
date: "2025-08-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install packages, include=FALSE}
source("utils/setup_packages.R")
install_packages_from_file()
```

```{r source util functions, include=FALSE}
source("utils/load_data.R")
source("LagAnalysis/lag_utils.R")
source("LagAnalysis/lag_functions.R")
source("LagAnalysis/stationarity_cointegration.R")
```

```{r libraries, include=FALSE}
library("tidyverse")
library("tsibble")
library("ggplot2")
library("scales")
library("ggh4x")
```

## Research Question

We examine the lead/lag structure of the individual indices relative to the main 
index in more detail. In doing so, we analyze the relationships between the 
indices both in general and specifically around turning points. The aim is to 
provide a comprehensive overview and to identify starting points for further 
research projects. In particular, we focus on identifying a subset of indices 
that explain the development of the main index especially well in advance.


## Correlation Analysis

### Data Basis for Correlation Analysis

The monthly data was analyzed in two seperate approaches:

- Full window based on data from **1991-01-01** to **2025-02-01**
- Rolling window with a **10 year window frame** and a **1 month step size**

For each Dataset we extract the correlation for each lag as well as the peak 
correlation across a lag of +/-6 months. The window of +/-6 months was specified
in discussion with the project partners to allow for a qualitative and causal 
interpretation. 

They choice for the rolling window size was mainly motivated by:finding a balance 
between:

- small enough window seize to detect changes over time, 
- large enough seize to not be heavily influence by trends (stationary)
- keep the computational demand within reasonable limits.


```{r Data Import, message=FALSE}
# Full Analysis Data
ccf_tbl_full <- read_csv("LagAnalysis/results/ccf_results_full.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = correlation)
ccf_tbl_full_peak <- read_csv("LagAnalysis/results/ccf_results_full_peak.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = peak_corr)
dcor_tbl_full <- read_csv("LagAnalysis/results/dcor_results_full.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = dcor)
dcor_tbl_full_peak <- read_csv("LagAnalysis/results/dcor_results_full_peak.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = peak_corr)
adf_tbl_full <- read_csv("LagAnalysis/results/adf_results_full.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3))

# Rolling Window Analysis Data
ccf_tbl_roll <- read_csv("LagAnalysis/results/ccf_results_roll.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = correlation)
ccf_tbl_roll_peak <- read_csv("LagAnalysis/results/ccf_results_roll_peak.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = peak_corr)
dcor_tbl_roll <- read_csv("LagAnalysis/results/dcor_results_roll.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>%
  rename(corr = dcor)
dcor_tbl_roll_peak <- read_csv("LagAnalysis/results/dcor_results_roll_peak.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3)) %>% 
  rename(corr = peak_dcor)
adf_tbl_roll <- read_csv("LagAnalysis/results/adf_results_roll.csv") %>%
  mutate(sector = str_sub(industry_code, 1, 3))
```


### Methods for the Analysis of Correlation Structure

We are not only interested in the mean... but rather the full distribution of 
correlation per industry and question values. 


Figure General Overview over Full Window


#### Lag Aggregation

As already shown in the full window plot the peak correlation for each question
lies within +/-6 months lag window. For several different parts of our analysis
we need to aggregate over the different lag windows. In this study we focused on 
two forms of aggreagtion:

- Peak Correlation of each industry code for lags between -6 and +6 months
- Mean Correlation of each industry code for lags between -6 and -1 months

The choice of these aggregation logics is mainly motivated by practical point of
view. To give a full overview over the correlation structure the peak correlation
offers are better reference point than the average correlation over a abitrary 
lag window. If we focus on predictability on the other hand, we want to limit
the correlation for lags between -6 to 1 months so that we analyze the predictive 
part of the correlation. 

Figure ... shows the difference between Mean and Peak Correlation in terms of...

```{r , warning=FALSE, echo=FALSE}
dcor_tbl_full %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         lag %in% c(-6:-1)) %>%
  group_by(indicator, industry_code, sector) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>% 
  # group_by(sector, indicator) %>%
  # summarise(mean_corr = mean(mean_corr), .groups = "drop") %>%
  ggplot(aes(x = indicator, y = mean_corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Average Distance Correlation distribution by Question",
    x = "Indicator (Question)",
    y = "Correlation"
  )

dcor_tbl_full_peak %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         peak_lag %in% c(-6:6)) %>%
  ggplot(aes(x = indicator, y = corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Peak Distance Correlation distribution by Question",
    x = "Indicator (Question)",
    y = "Correlation"
  )
```


#### Dcor vs CCF

To validate the findings the correlation between the individual time series and
the main index (*C0000000 - KLD*) was analyzed with two different approaches:

- Cross Correlation using **stats::ccf**
- Distance Correlation using **energy::dcor**

The distance correlation can be seen as an upper bound for the cross correlation 
function that measures the linear dependence between the different time series. 
For our analysis the main benefit of the distance correlation is the ability to 
verify our Cross Correlation Results as well as having a "un-directed" correlation
measure. 

Figure ... shows the difference between CCF and Dcor
```{r CCF and DCor, echo=FALSE, warning=FALSE}
# Filter ccf Results
heatmap_data <- ccf_tbl_full %>%
  filter(difference==0,
         level > 0) %>%
  compute_balanced_median

# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(median_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot ccf Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(x = lag, y = indicator, fill = median_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Average Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")


# Dcor Overview
heatmap_data <- dcor_tbl_full %>%
  filter(difference==0,
         level > 0) %>%
  group_by(lag, indicator) %>%
  summarise(median_corr = median(corr, na.rm = TRUE), .groups = "drop")


# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(median_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot dcor Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(x = lag, y = indicator, fill = median_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Average Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")
```

The CCF and the Dcor analysis show a fairly similar picture of the correlation 
structure. With the main difference being that the distance correlation only 
captures the absolute dependency and not its direction.



#### Industry Aggregation

The hierarchical tree structure from the data introduces an inherent imbalance
into aggregation over industry codes of different sectors (2 digit codes). 
This imbalance stems from the different granularity in the aggregation of the 
industry codes. Sectors with a higher granularity have a deeper tree structure 
with more leaf nodes than smaller sectors. 

The following plot contains amount of unique industry codes per sector, showing 
the imbalances between between the different sector: 
```{r Balanced Aggregation, warning=FALSE}
ccf_tbl_full %>%
  filter(level > 0,
         difference == 0) %>%
  distinct(industry_code, sector, level) %>%
  ggplot(aes(x = sector, fill = factor(level))) +
  geom_bar(position = "stack") +
  theme_minimal() +
  labs(
    title = "Number of Industry Codes by Level",
    x = "Sector",
    y = "Count",
    fill = "Level"
  )
```

For our correlation analysis this poses a challenge in the context that we are 
indirectly weight the sectors by their granularity. Since we are likely to 
include multiple industry codes from sectors with a good correlation and high 
granularity and thereby weigh them higher than sectors with a good correlation 
but low granularity. Thereby effectively limiting the potential contribution of 
sectors with a lower granularity. 

To avoid this imbalance influencing we will average over the sectors, when 
calculating the correlation between the different questions and the main index.

```{r, message=FALSE}
compute_balanced_median <- function(df){
  df %>%
  summarise(sector_median = mean(corr, na.rm = TRUE), 
            .by = c(lag, indicator, sector)) %>%
  summarise(median_corr  = mean(sector_median,  na.rm = TRUE), 
            .by = c(lag, indicator))
}
```


#### Development over time

To get a better overview over the development of the correlation over time we 
analyzed the correlation in a 10 years rolling window with 1 month step size. 

The following graph gives a broad overview over the change in correlation from the
early 1990's to 2025. The time scale start in 2000 with the first complete 10 year
window. 
While this broad overview does not yet allow for any qualitative deductions, we 
can already see similar patterns and changes across the time domain as well as 
the different questions...

```{r}
# Filter ccf Results
heatmap_data <- ccf_tbl_roll %>%
  filter(difference==0,
         level %in% c(1:3)) %>% 
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(correlation, na.rm = TRUE), .groups = "drop")

# Plot ccf Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Average Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")
```

While the KLD Series Peak Correlation stays the same over time, the other questions
show at least small changes in the lag of the Peak Correlation over time. 

```{r}
# Filter ccf Results
heatmap_data <- ccf_tbl_roll %>%
  filter(difference==0,
         level %in% c(1:3),
         lag %in% c(-6:6)) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(correlation, na.rm = TRUE), .groups = "drop")

# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator, date_window_end) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot ccf Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Average Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")
```

Next we want to better understand the development of the Mean and Variance of our
Correlation over time. Since we are only interested in the strength of the 
correlation and not the direction, we use the distance correlation as basis for
our Analysis.

```{r, warning=FALSE, echo=FALSE}
dcor_tbl_roll %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(dcor, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Development of Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )

dcor_tbl_roll_peak %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         peak_lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(peak_dcor, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Development of Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```

As we can see the median of both the average correlation within +/-6 months lag, 
as well as the peak correlation within +/-6 months lag behave fairly similar over 
time. Based on the quantile bands we can also see that there probably exists a 
subset of industry codes that have a higher correlation across all questions and
the time domain. 
The next step is to find a fitting subset and analyze how much this subset 
overlaps with the Top correlated industry codes from the full window analysis.



### Correlation Structure between Levels

```{r, warning=FALSE, echo=FALSE}
dcor_tbl_full %>% 
  filter(level > 0, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(level, industry_code) %>%
  summarise(mean_corr = mean(dcor, na.rm = TRUE), .groups = "drop") %>% 
  ggplot(aes(x = factor(level), y = mean_corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Average Distance Correlation distribution by Level",
    x = "Level",
    y = "Correlation"
  )


dcor_tbl_full_peak %>% 
  filter(level > 0, 
         difference == 0) %>%
  group_by(level, sector) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(x = factor(level), y = mean_corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Average Distance Correlation distribution by Level",
    x = "Level",
    y = "Correlation"
  )
  
```

While we still have a acceptable variance in the deeper Levels we do lack the 
interpretability from an economic point of view. Since there are now major 
differences in the correlation it is safe for us to exclude the levels 4 and 5 
from our further analysis. 


### Consitency of Correlation Structure 

To see whether we can focuse the on top correlated indices, we closer 
investigate the ranking of indices by correlation and its stability across the 
different indicators and levels. 
We quantify the stability by using the jaccard consensus of the **k** top ranked 
industry codes. To find a good **k** as limit for our focused correlation 
analysis we plot the consenus as well as the absolute overlap between the 
different indicators (questions) across multiple k values.


```{r, warning=FALSE, echo=FALSE}
# Extract Ranking for our dcor values
dcor_tbl_full_rank <- dcor_tbl_full_peak %>%
  filter(level %in% c(1:3),
         difference == 0) %>%
  group_by(indicator) %>%
  mutate(rank = rank(-corr, ties.method = "min")) %>%
  arrange(indicator, rank) %>%
  ungroup()

k_vec <- seq.int(10,130,10)

# Calculate Jaccard Consenus between Indicators
jac_curve <- dcor_tbl_full_rank %>%
  compute_topk_jaccard(k_vec) %>%
  rename(value = mean_jacc) %>%
  mutate(metric = "Mean Jaccard")

# Calculate overlap between Indicatos
overlap_curve <- dcor_tbl_full_rank %>%
  compute_topk_overlap(k_vec) %>%
  rename(value = overlap) %>%
  mutate(metric = "Union size")

plot_data <- jac_curve %>%
  bind_rows(overlap_curve)

ggplot(plot_data, aes(x = k, y = value, color = metric)) +
  geom_line() +
  geom_point() +
  facet_wrap(~metric, scales = "free_y") +
  theme_minimal() +
  labs(title = "Consensus & Overlap across top-k sets",
       x = "k (top industries)",
       y = NULL)
```

This shows us that the size of the union and therefore the amount of industry 
codes we need to take into account, grows quite rapidly in the beginning and 
after *k = 50*. For *k = 50* we achieve a decent consensus, while still keeping 
a relatively small union size. We also see that for *k < 30* the consensus drops 
quite rapidly, which indicates that the composition of the rankings start to 
differ quite drasticly at least for some indicator pairs. 

Based on this findings we want to limit analysis of the top correlating 
industries on the top 30 - 50 ranked industry codes. But need further analysis 
to find the ideal *k*-value.

To better compare implications of the different *k*-values we can plot the 
Box Plot for our Limits *k* = 30 and *k* = 50.

```{r, echo=FALSE}
# Top 30 ranked Industry Codes per question
top30 <- dcor_tbl_full_rank %>%
  filter(rank <= 30) %>%
  pull(industry_code) %>%
  unique()

# Top 30
dcor_tbl_full_peak %>% 
  filter(difference == 0,
         peak_lag %in% c(-6:6),
         industry_code %in% top30) %>%
  ggplot(aes(x = indicator, y = corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Top 30 - Peak Distance Correlation distribution by Question",
    x = "Indicator (Question)",
    y = "Correlation"
  )
```

As we can see from the plot *k* = 30 helps us to drastically reduce the variance
of our plotted correlations. We also see that the distribution of correlation has
a heavier tail with frequent outliers on the lower correlation side. 
Since the heavy lower tail skews the mean calculation, it makes sense to use the 
median for our aggregation instead.
So for the further analysis we will us *k* = 30 and the median as aggreagtion.


### Ranking Analysis

- To detect variability within Data. 
- Analysis of consitency of ranking. 
- Top 30 gives small enough set size to detect changes, but still bigh enough to 
not be dominated by noise

```{r}
# Extract Ranking for our dcor values
dcor_tbl_roll_rank <- dcor_tbl_roll_peak %>%
  filter(level %in% c(1:3),
         difference == 0) %>%
  group_by(indicator, window_id) %>%
  mutate(rank = rank(-corr, ties.method = "min")) %>%
  arrange(indicator, window_id, rank) %>%
  ungroup()

k_vec <- c(1,seq.int(10,130,10))

# Calculate Jaccard Consenus between Windows
jac_curve <- dcor_tbl_roll_rank %>%
  group_by(indicator) %>%
  group_modify(~ compute_topk_jaccard_win(.x, k_vec)) %>%
  rename(value = mean_jacc) %>%
  mutate(metric = "Mean Jaccard")

# Calculate overlap between Indicatos
overlap_curve <- dcor_tbl_roll_rank %>%
  group_by(indicator) %>%
  group_modify(~ compute_topk_overlap(.x, k_vec)) %>%
  rename(value = overlap) %>%
  mutate(metric = "Union size")

plot_data <- jac_curve %>%
  bind_rows(overlap_curve)

# Plots
plot_data %>%
  filter(metric=="Mean Jaccard") %>%
  ggplot(aes(x = k, y = value)) +
  geom_line(color = "#F8766D") +
  geom_point(color = "#F8766D") +
  geom_point(
    data = . %>% filter(k == 30),  # only keep k = 30
    aes(x = k, y = value),
    color = "red", size = 2
  ) +
  facet_wrap(~indicator) +
  theme_minimal() +
  labs(title = "Consensus across top-k sets per Indicator",
       x = "k (top industries)",
       y = NULL)

plot_data %>%
  filter(metric=="Union size") %>%
  ggplot(aes(x = k, y = value)) +
  geom_line(color = "#00BFC4") +
  geom_point(colour = "#00BFC4") +
  geom_point(
    data = . %>% filter(k == 30),  # only keep k = 30
    aes(x = k, y = value),
    color = "red", size = 2
  ) +
  facet_wrap(~indicator) +
  theme_minimal() +
  labs(title = "Overlap across top-k sets per Indicator",
       x = "k (top industries)",
       y = NULL)


```
Now that we have established that *k* = 30 is still a viable cutoff point. 
We want to evaluate the consistency off our Top k set over time.


```{r}
k_vec <- 30

# Calculate Jaccard Consenus between Windows
jac_curve <- dcor_tbl_roll_rank %>%
  group_by(date_window_end) %>%
  group_modify(~ compute_topk_jaccard(.x, k_vec)) %>%
  rename(value = mean_jacc) %>%
  mutate(metric = "Mean Jaccard")

# Calculate overlap between Indicatos
overlap_curve <- dcor_tbl_roll_rank %>%
  group_by(date_window_end) %>%
  group_modify(~ compute_topk_overlap(.x, k_vec)) %>%
  rename(value = overlap) %>%
  mutate(metric = "Union size")

plot_data <- jac_curve %>%
  bind_rows(overlap_curve)

ggplot(plot_data, aes(x = date_window_end, y = value, color = metric)) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_wrap(~metric, scales = "free_y") +
  theme_minimal() +
  labs(title = "Consensus & Overlap across top-k sets",
       x = "k (top industries)",
       y = NULL)
```



Based on these results
If we now take the union of these sets over all windows we quickly see that
almost all industry codes are in the top 30 at least one time. This solidifies 
that there .....

```{r}
# Top 30 ranked Industry Codes per question
top30_roll <- dcor_tbl_roll_rank %>%
  filter(rank <= 1) %>%
  pull(industry_code) %>%
  unique()
```



## Prediction

To find a good subset of industry codes that combine interpretability with
predictive power...
Allow for qualitative assessment but still yield similar predictive power to a
quantitative analysis. 

```{r}

top30_ind <- top30 %>% 
  group_by(industry_code) %>% 
  count() %>% 
  filter(n >= 10)
top30_intersect <- top30 %>% 
  filter(industry_code %in% top30_ind$industry_code) %>% 
  group_by(indicator) %>% 
  count()
  
```


```{r}
peak_dcor <- dcor_tbl_roll_peak %>%
  filter(level %in% c(1:3)) %>%
  group_by(indicator, date_window_end) %>%
  slice_max(corr, n = 1, with_ties = FALSE) %>%
  select(indicator, date_window_end, corr) %>%
  rename(peak_corr = corr)


```

================================================================================
###
Avg correlation auf -6:0 ändern! 
Peak bei -6:6!

###
- Level 50 gute performance! Gute early Indicators?

###
Compare with over all Top 30 set!!!
Picture of Jaccard function
-> Set Size too big in Rolling Window Analysis
-> Score Based Selection (Residual to Top for each Question avg. over Windows)

#######
- by sector analyse

####

Over all Questions (Peak thing)
- Set highly correlated
- Set low correlated
- Set high variance


Best Predictor (-6:-1)
- Set best predictor 


Best early predictor (-6:-4)
- Set best predictor 

By BB Tunring Points
- 