---
title: "lag_report"
output: html_document
date: "2025-08-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install packages, include=FALSE}
source("utils/setup_packages.R")
install_packages_from_file()
```

```{r source util functions, include=FALSE}
source("utils/load_data.R")
source("LagAnalysis/lag_utils.R")
source("LagAnalysis/lag_functions.R")
source("LagAnalysis/stationarity_cointegration.R")
```

```{r libraries, include=FALSE}
library("tidyverse")
library("tsibble")
library("ggplot2")
library("scales")
library("glmnet")
```


## Correlation Analysis

### Data Basis for Correlation Analysis

```{r Data Import, include=FALSE}
# Full Analysis Data
ccf_tbl_full <- read_csv("LagAnalysis/results/ccf_results_full.csv")
ccf_tbl_full_peak <- read_csv("LagAnalysis/results/ccf_results_full_peak.csv")
dcor_tbl_full <- read_csv("LagAnalysis/results/dcor_results_full.csv")
dcor_tbl_full_peak <- read_csv("LagAnalysis/results/dcor_results_full_peak.csv")
adf_tbl_full <- read_csv("LagAnalysis/results/adf_results_full.csv")

# Rolling Window Analysis Data
ccf_tbl_roll <- read_csv("LagAnalysis/results/ccf_results_roll.csv") 
ccf_tbl_roll_peak <- read_csv("LagAnalysis/results/ccf_results_roll_peak.csv")
dcor_tbl_roll <- read_csv("LagAnalysis/results/dcor_results_roll.csv")
dcor_tbl_roll_peak <- read_csv("LagAnalysis/results/dcor_results_roll_peak.csv")
adf_tbl_roll <- read_csv("LagAnalysis/results/adf_results_roll.csv")
```



### Methods for the Analysis of Correlation Structure

#### Industry Aggregation

**Hierarchical Aggreagtion:**

```{r Industries per Sector, warning=FALSE}
ccf_tbl_full %>%
  filter(level > 0,
         difference == 0) %>%
  distinct(industry_code, sector, level) %>%
  ggplot(aes(x = sector, fill = fct_rev(factor(level)))) +
  geom_bar(position = "stack") +
  theme_minimal() +
  labs(
    title = "Number of Industry Codes by Sector",
    x = "Sector",
    y = "Count",
    fill = "Level"
  )

counts_by_sector_level <- ccf_tbl_full %>%
  distinct(sector, level, industry_code) %>%  # 1 row per code
  count(sector, level, name = "n_codes") %>%  # #codes per sector x level
  filter(level >= 2)                           # L1 omitted (always 1)

ggplot(counts_by_sector_level, aes(x = factor(level), y = n_codes)) +
  #geom_violin(trim = FALSE, alpha = 0.3) +
  geom_boxplot(width = 0.2, outlier.shape = NA) +
  geom_jitter(width = 0.08, height = 0, alpha = 1, size = 1, color = "blue") +
  labs(title = "Dispersion of Industries per Sector by Level",
       x = "Level", y = "Number of Industries per Sector") +
  theme_minimal()
```

**Level Restriction**

Plot Industrie codes per Level

```{r Industries per Level}
ccf_tbl_full %>%
  filter(level > 0,
         difference == 0) %>%
  distinct(industry_code, level) %>%
  ggplot(aes(x = level, fill = factor(level))) +
  geom_bar(position = "stack") +
  theme_minimal() +
  labs(
    title = "Number of Industry Codes by Level",
    x = "Sector",
    y = "Count",
    fill = "Level"
  )
```


### Full Window Analysis

**General Overview**

Plot: CCF and Dcor

```{r CCF and DCor, echo=FALSE, warning=FALSE}
# Filter ccf Results
heatmap_data <- ccf_tbl_full %>%
  filter(difference==0,
         level > 0) %>%
  summarise(median_corr = median(corr, na.rm = TRUE), 
            .by = c(lag, indicator))

# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(median_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot ccf Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(x = lag, y = indicator, fill = median_corr)) +
  geom_tile() +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed", size = 0.6) +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Median Cross Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Median Corr")


# Dcor Overview
heatmap_data <- dcor_tbl_full %>%
  filter(difference==0,
         level > 0) %>%
  summarise(median_corr = median(corr, na.rm = TRUE), 
            .by = c(lag, indicator))


# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(median_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot dcor Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(x = lag, y = indicator, fill = median_corr)) +
  geom_tile() +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed", size = 0.6) +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient(low = "white", high = "red", 
                       limits = c(0, 1)) +
  theme_minimal() +
  labs(title = "Median Distance Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Median Corr")
```


**Correlation Distribution by Question**

Plot: Correlation Distribution by Question

```{r Distribution by Indicator, warning=FALSE, echo=FALSE}
dcor_tbl_full %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         lag %in% c(-6:-1)) %>%
  group_by(indicator, industry_code, sector) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>% 
  # group_by(sector, indicator) %>%
  # summarise(mean_corr = mean(mean_corr), .groups = "drop") %>%
  ggplot(aes(x = indicator, y = mean_corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Average Distance Correlation distribution by Question",
    x = "Indicator (Question)",
    y = "Correlation"
  )

dcor_tbl_full_peak %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         lag %in% c(-6:6)) %>%
  ggplot(aes(x = indicator, y = corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Peak Distance Correlation distribution by Question",
    x = "Indicator (Question)",
    y = "Correlation"
  )
```


**Correlation Distribution by Sectors**

Plot: Distribution by Sectors

```{r Distribution by Sector, warning=FALSE, echo=FALSE}
dcor_tbl_full %>% 
  filter(level > 0, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(level, sector) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(x = factor(sector), y = mean_corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Average Distance Correlation distribution by Sector",
    x = "Level",
    y = "Correlation"
  )


dcor_tbl_full_peak %>% 
  filter(level > 0, 
         difference == 0) %>%
  group_by(level, sector) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(x = factor(level), y = mean_corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Average Peak Distance Correlation distribution by Level",
    x = "Level",
    y = "Correlation"
  )
  
```



**Correlation Distribution by Levels**

Plot: Distribution over Levels

```{r Distribution over Level, warning=FALSE, echo=FALSE}
dcor_tbl_full %>% 
  filter(level > 0, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(sector, industry_code, indicator) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(x = sector, y = mean_corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Average Distance Correlation distribution by Sector",
    x = "Sector",
    y = "Distance Correlation"
  )


dcor_tbl_full_peak %>% 
  filter(level > 0, 
         difference == 0) %>%
  ggplot(aes(x = sector, y = corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Average Peak Distance Correlation distribution by Sector",
    x = "Sector",
    y = "Distance Correlation"
  )
  
```


### Development over time

**General Overview** 

Plot:  CCF Rolling Window

```{r CCF Rolling Window}
# Filter ccf Results
heatmap_data <- ccf_tbl_roll %>%
  filter(difference==0,
         level %in% c(1:3)) %>% 
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")

# Plot ccf Results
ggplot(heatmap_data, aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Average Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")
```
 

```{r CCF Rolling Window + Peak}
# Filter ccf Results
heatmap_data <- ccf_tbl_roll %>%
  filter(difference==0,
         level %in% c(1:3),
         lag %in% c(-6:6)) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")

# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator, date_window_end) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot ccf Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  geom_tile(data = highlight_points,
            color = "yellow", size = 0.1, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Average Cross Correlation per Lag and Indicator (Peak highlighted)",
       x = "Window End Date",
       y = "Lag",
       fill = "Mean Corr")
```


**Correlation Distribution by Question**

```{r Distribiton by Indicator, warning=FALSE, echo=FALSE}
dcor_tbl_roll %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Development of Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )

dcor_tbl_roll_peak %>% 
  filter(level %in% c(1:3), 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Development of Peak Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```



**Correlation Distribution by Sectors**


**Correlation Distribution by Levels**

```{r Distribiton by Levels, warning=FALSE, echo=FALSE}
dcor_tbl_roll %>% 
  filter(level > 0, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(level, indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(level, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ level) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Development of Correlation distribution by Level",
    x = "Date Window End",
    y = "Distance Correlation"
  )

dcor_tbl_roll_peak %>% 
  filter(level > 0, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(level, indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(level, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ level) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Development of Peak Correlation distribution by Level",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```


### Consitency of Correlation Structure 

**Full Window Analysis**

Plot: Consensus and Overlap for Full Window Analysis

```{r Consensus and Overlap (Full), warning=FALSE, echo=FALSE}
# Extract Ranking for our dcor values
dcor_tbl_full_rank <- dcor_tbl_full_peak %>%
  filter(level %in% c(1:3),
         difference == 0) %>%
  group_by(indicator) %>%
  mutate(rank = rank(-corr, ties.method = "min")) %>%
  arrange(indicator, rank) %>%
  ungroup()

k_vec <- c(1, seq.int(10,130,10))

# Calculate Jaccard Consenus between Indicators
jac_curve <- dcor_tbl_full_rank %>%
  compute_topk_jaccard(k_vec) %>%
  rename(value = mean_jacc) %>%
  mutate(metric = "Mean Jaccard")

# Calculate overlap between Indicatos
overlap_curve <- dcor_tbl_full_rank %>%
  compute_topk_overlap(k_vec) %>%
  rename(value = overlap) %>%
  mutate(metric = "Union size")

plot_data <- jac_curve %>%
  bind_rows(overlap_curve)

ggplot(plot_data, aes(x = k, y = value, color = metric)) +
  geom_line() +
  geom_point() +
  facet_wrap(~metric, scales = "free_y") +
  theme_minimal() +
  labs(title = "Consensus & Overlap across top-k sets",
       x = "k (top industries)",
       y = NULL)
```


```{r Top 30 Distrution by Indicator, echo=FALSE}
# Top 30 ranked Industry Codes per question
top30 <- dcor_tbl_full_rank %>%
  filter(rank <= 30) %>%
  pull(industry_code) %>%
  unique()

# Top 30
dcor_tbl_full_peak %>% 
  filter(difference == 0,
         lag %in% c(-6:6),
         industry_code %in% top30) %>%
  ggplot(aes(x = indicator, y = corr)) +
  # facet_wrap(~ indicator) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Top 30 - Peak Distance Correlation distribution by Question",
    x = "Indicator (Question)",
    y = "Correlation"
  )
```


**Rolling Window Analysis**

Plot: Consensus and Overlap by Indicator

```{r Consensus and Overlap (Roll), warning=FALSE, echo=FALSE}
# Extract Ranking for our dcor values
dcor_tbl_roll_rank <- dcor_tbl_roll_peak %>%
  filter(level %in% c(1:3),
         difference == 0) %>%
  group_by(indicator, window_id) %>%
  mutate(rank = rank(-corr, ties.method = "min")) %>%
  arrange(indicator, window_id, rank) %>%
  ungroup()

k_vec <- c(1,seq.int(10,130,10))

# Calculate Jaccard Consenus between Windows
jac_curve <- dcor_tbl_roll_rank %>%
  group_by(indicator) %>%
  group_modify(~ compute_topk_jaccard_win(.x, k_vec)) %>%
  rename(value = mean_jacc) %>%
  mutate(metric = "Mean Jaccard")

# Calculate overlap between Indicatos
overlap_curve <- dcor_tbl_roll_rank %>%
  group_by(indicator) %>%
  group_modify(~ compute_topk_overlap(.x, k_vec)) %>%
  rename(value = overlap) %>%
  mutate(metric = "Union size")

plot_data <- jac_curve %>%
  bind_rows(overlap_curve)

# Plots
plot_data %>%
  filter(metric=="Mean Jaccard") %>%
  ggplot(aes(x = k, y = value)) +
  geom_line(color = "#F8766D") +
  geom_point(color = "#F8766D") +
  geom_point(
    data = . %>% filter(k == 30),  # only keep k = 30
    aes(x = k, y = value),
    color = "red", size = 2
  ) +
  facet_wrap(~indicator) +
  theme_minimal() +
  labs(title = "Consensus across top-k sets per Indicator",
       x = "k (top industries)",
       y = NULL)

plot_data %>%
  filter(metric=="Union size") %>%
  ggplot(aes(x = k, y = value)) +
  geom_line(color = "#00BFC4") +
  geom_point(colour = "#00BFC4") +
  geom_point(
    data = . %>% filter(k == 30),  # only keep k = 30
    aes(x = k, y = value),
    color = "red", size = 2
  ) +
  facet_wrap(~indicator) +
  theme_minimal() +
  labs(title = "Overlap across top-k sets per Indicator",
       x = "k (top industries)",
       y = NULL)


```

Plot: Concensus and Overlap over time window for k=30

```{r Consensus and Overlap by Window, warning=FALSE, echo=FALSE}
k_vec <- 30

# Calculate Jaccard Consenus between Windows
jac_curve <- dcor_tbl_roll_rank %>%
  group_by(date_window_end) %>%
  group_modify(~ compute_topk_jaccard(.x, k_vec)) %>%
  rename(value = mean_jacc) %>%
  mutate(metric = "Mean Jaccard")

# Calculate overlap between Indicatos
overlap_curve <- dcor_tbl_roll_rank %>%
  group_by(date_window_end) %>%
  group_modify(~ compute_topk_overlap(.x, k_vec)) %>%
  rename(value = overlap) %>%
  mutate(metric = "Union size")

plot_data <- jac_curve %>%
  bind_rows(overlap_curve)

ggplot(plot_data, aes(x = date_window_end, y = value, color = metric)) +
  geom_line() +
  geom_point(size = 0.5) +
  facet_wrap(~metric, scales = "free_y") +
  theme_minimal() +
  labs(title = "Consensus & Overlap across top-k sets",
       x = "Date Window End",
       y = NULL,
       color = "Metric")
```



**Set Size of Top k Industry Codes**

```{r Top k Set Size}
# Top 30 ranked Industry Codes per question
k_vec <- c(1,seq.int(10,130,10))

uniq_by_k <- map_dfr(k_vec, ~
  dcor_tbl_roll_rank %>%
    filter(rank <= .x) %>%
    summarise(k = .x,
              n_unique_industries = n_distinct(industry_code))
)

# Plot
uniq_by_k %>%
  ggplot(aes(x = k, y = n_unique_industries)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "k (Rank Cutoff)", y = "Distinct Industries")
```


### Score Calculation

**Residual Calculation**

Table: Residuals

```{r Residual Calculation}
peak_dcor <- dcor_tbl_roll_peak %>%
  filter(level > 0,
         difference==0) %>%
  group_by(indicator, date_window_end) %>%
  slice_max(corr, n = 1, with_ties = FALSE) %>%
  select(indicator, date_window_end, corr) %>%
  rename(peak_corr = corr)

res_dcor <- dcor_tbl_roll_peak %>%
  filter(level > 0,
         difference==0) %>%
  left_join(peak_dcor, by = join_by(indicator, date_window_end)) %>%
  mutate(res_corr = (peak_corr-corr)^2)

res_dcor %>% 
  select(industry_code, indicator, window_id,  corr, peak_corr, res_corr) %>%
  head()
```


**Score Calculation and Distribution**

Figure: Distribution of Score and Variance per Sector

```{r Score calculation & distribution}
score_tbl_roll <- res_dcor %>%
  group_by(industry_code, level, sector) %>%
  summarise(score = 1-mean(res_corr),
            var = var(res_corr),
            .groups = "drop") %>%
  arrange(desc(score))

score_tbl_roll %>% 
  ggplot(aes(x = sector, y = score)) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Score by Peak Correlation",
    x = "Sector",
    y = "Score"
  )

score_tbl_roll %>% 
  ggplot(aes(x = sector, y = var)) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Variance of Score by Peak Correlation",
    x = "Sector",
    y = "Variance"
  )

score_tbl_roll %>% 
  ggplot(aes(x = factor(level), y = score)) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Score by Peak Correlation",
    x = "Sector",
    y = "Variance"
  )

```


**Top-k Set Performance**

Plot: Avg. and minimum score of Top-k industries (ranked by score)

```{r}
score_tbl_roll %>%                       # your 5‑col table
  arrange(desc(score)) %>%
  mutate(k = row_number(),
         avg_topk = cummean(score),
         min_topk = cummin(score)) %>%
  ggplot(aes(x = k)) +
  geom_line(aes(y = min_topk), color = "#F8766D") +
  geom_point(aes(y = min_topk), color = "#F8766D", size = 0.25) +
  geom_line(aes(y = avg_topk), color = "#00BFC4") +
  geom_point(aes(y = avg_topk), color = "#00BFC4", size = 0.75) +
  theme_minimal() +
  labs(title = "Average and minimum score of top k set",
       x = "k (top k by score)", y = "Score")
```

- Plot shows the avg. and minimum scores of the Top-k sets
- After the set of top 25 industries the avg and minimum score drop a lot faster
- The bottom 25 industries have significant lower score values
- Based on plot 5, and 25 are good set sizes for further analysis both of 
top and bottom industries


#### Set Analysis

- Identification of interesting sets for further research
- Focus on points of view
  - Sets that capture the full picture well
  - Sets that allows for early predictions
  - Level 4 and 5

##### Full Picture Analysis

**Highly Correlated Industries**
Plot: Top 5
```{r}
# Top Industries
top05_peak <- score_tbl_roll %>%
  filter(level %in% c(1:3)) %>%
  slice_max(score, n=5, with_ties = FALSE) %>%
  pull(industry_code)

#Plot CCF Full Window
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% top05_peak,
         difference==0) %>%
  group_by(indicator, lag) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")
  
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

ggplot(heatmap_data, aes(x = lag, y = indicator, fill = mean_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Top 5 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")


# Plot ccf Results Roll
ccf_tbl_roll %>%
  filter(industry_code %in% top05_peak,
         difference==0) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = " Top 5 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Date Window End",
       y = "Indicator",
       fill = "Mean Corr")

# Plot Distribution by Question
dcor_tbl_roll_peak %>% 
  filter(industry_code %in% top05_peak, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = " Top 5 - Development of Peak Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```


Plot: Top 25
```{r Top 25 Peak}
# Top Industries
top25_peak <- score_tbl_roll %>%
  filter(level %in% c(1:3)) %>%
  slice_max(score, n=25, with_ties = FALSE) %>%
  pull(industry_code)

#Plot CCF Full Window
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% top25_peak,
         difference==0) %>%
  group_by(indicator, lag) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")
  
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

ggplot(heatmap_data, aes(x = lag, y = indicator, fill = mean_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Top 25 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")


# Plot ccf Results Roll
ccf_tbl_roll %>%
  filter(industry_code %in% top25_peak,
         difference==0) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = " Top 25 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")

# Plot Distribution by Question
dcor_tbl_roll_peak %>% 
  filter(industry_code %in% top25_peak, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = " Top 25 - Development of Peak Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```


**Low Correlated Industries**
Plot: Low 5
```{r Low 5 Peak}
# Top Industries
low05_peak <- score_tbl_roll %>%
  filter(level %in% c(1:3)) %>%
  slice_min(score, n=5, with_ties = FALSE) %>%
  pull(industry_code)

#Plot CCF Full Window
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% low05_peak,
         difference==0) %>%
  group_by(indicator, lag) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")
  
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

ggplot(heatmap_data, aes(x = lag, y = indicator, fill = mean_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Bottom 5 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Date Window End",
       y = "Indicator",
       fill = "Mean Corr")


# Plot ccf Results Roll
ccf_tbl_roll %>%
  filter(industry_code %in% low05_peak,
         difference==0) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = " Bottom 5 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Date Window End",
       y = "Indicator",
       fill = "Mean Corr")

# Plot Distribution by Question
dcor_tbl_roll_peak %>% 
  filter(industry_code %in% low05_peak, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = " Bottom 5 - Development of Peak Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```


Plot: Low 25
```{r Low 25 Peak}
# Top Industries
low25_peak <- score_tbl_roll %>%
  filter(level %in% c(1:3)) %>%
  slice_min(score, n=25, with_ties = FALSE) %>%
  pull(industry_code)

#Plot CCF Full Window
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% low25_peak,
         difference==0) %>%
  group_by(indicator, lag) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")
  
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

ggplot(heatmap_data, aes(x = lag, y = indicator, fill = mean_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Bottom 25 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")


# Plot ccf Results Roll
ccf_tbl_roll %>%
  filter(industry_code %in% low25_peak,
         difference==0) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = " Bottom 25 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")

# Plot Distribution by Question
dcor_tbl_roll_peak %>% 
  filter(industry_code %in% low25_peak, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = " Bottom 25 - Development of Peak Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```


**High Variance Industriess**

Plot: Var Top 5

```{r Variance Top 5 Peak}
# Top Industries
var05_peak <- score_tbl_roll %>%
  filter(level %in% c(1:3)) %>%
  slice_max(var, n=5, with_ties = FALSE) %>%
  pull(industry_code)

#Plot CCF Full Window
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% var05_peak,
         difference==0) %>%
  group_by(indicator, lag) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")
  
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

ggplot(heatmap_data, aes(x = lag, y = indicator, fill = mean_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "High Variance - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")


# Plot ccf Results Roll
ccf_tbl_roll %>%
  filter(industry_code %in% var05_peak,
         difference==0) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = " High Variabce - Avg. Cross-Correlation per Lag and Indicator",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")

# Plot Distribution by Question
dcor_tbl_roll_peak %>% 
  filter(industry_code %in% var05_peak, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = " High Variance - Development of Peak Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```


Plot: Var Top 25

```{r Variance Top 25 Peak}
# Top Industries
var25_peak <- score_tbl_roll %>%
  filter(level %in% c(1:3)) %>%
  slice_max(var, n=25, with_ties = FALSE) %>%
  pull(industry_code)

#Plot CCF Full Window
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% var25_peak,
         difference==0) %>%
  group_by(indicator, lag) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")
  
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

ggplot(heatmap_data, aes(x = lag, y = indicator, fill = mean_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "High Variance - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")


# Plot ccf Results Roll
ccf_tbl_roll %>%
  filter(industry_code %in% var25_peak,
         difference==0) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = " High Variabce - Avg. Cross-Correlation per Lag and Indicator",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")

# Plot Distribution by Question
dcor_tbl_roll_peak %>% 
  filter(industry_code %in% var25_peak, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = " High Variance - Development of Peak Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```


**Level 4 & 5**

Plot: 

```{r Level 4 & 5}
top05_level_peak <- score_tbl_roll %>%
  filter(level %in% c(4:5)) %>%
  slice_max(score, n=5, with_ties = FALSE) %>%
  pull(industry_code)

#Plot CCF Full Window
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% top05_level_peak,
         difference==0) %>%
  group_by(indicator, lag) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")
  
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

ggplot(heatmap_data, aes(x = lag, y = indicator, fill = mean_corr)) +
  geom_tile() +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "High Variance - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")


# Plot ccf Results Roll
ccf_tbl_roll %>%
  filter(industry_code %in% top05_level_peak,
         difference==0) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = " High Variabce - Avg. Cross-Correlation per Lag and Indicator",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")

# Plot Distribution by Question
dcor_tbl_roll_peak %>% 
  filter(industry_code %in% top05_level_peak, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = " High Variance - Development of Peak Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```


##### Predictive Sets

**Best Predictor (-6:-1)**

```{r Score Predictors}
peak_dcor <- dcor_tbl_roll_peak %>%
  filter(level > 0,
         difference==0) %>%
  group_by(indicator, date_window_end) %>%
  slice_max(corr, n = 1, with_ties = FALSE) %>%
  select(indicator, date_window_end, corr) %>%
  rename(peak_corr = corr)

res_dcor <- dcor_tbl_roll %>%
  filter(level > 0,
         difference==0,
         lag %in% c(-6:-1)) %>%
  group_by(indicator, date_window_end, industry_code, level, sector) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  left_join(peak_dcor, by = join_by(indicator, date_window_end)) %>%
  mutate(res_corr = (peak_corr-mean_corr)^2)

score_tbl_roll <- res_dcor %>%
  group_by(industry_code, level, sector) %>%
  summarise(score = 1-mean(res_corr),
            var = var(res_corr),
            .groups = "drop") %>%
  arrange(desc(score))

score_tbl_roll %>% 
  ggplot(aes(x = sector, y = score)) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Score by Peak Correlation",
    x = "Sector",
    y = "Score"
  )

score_tbl_roll %>% 
  ggplot(aes(x = sector, y = var)) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Variance of Score by Peak Correlation",
    x = "Sector",
    y = "Variance"
  )

score_tbl_roll %>% 
  ggplot(aes(x = factor(level), y = score)) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Score by Peak Correlation",
    x = "Sector",
    y = "Variance"
  )

```
```{r Plot Predictors}
# Top Industries
top05_pred <- score_tbl_roll %>%
  filter(level %in% c(2)) %>%
  slice_max(score, n=5, with_ties = FALSE) %>%
  pull(industry_code)

top25_pred <- score_tbl_roll %>%
  filter(level %in% c(2)) %>%
  slice_max(score, n=25, with_ties = FALSE) %>%
  pull(industry_code)

#Plot CCF Full Window
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% top05_pred,
         difference==0) %>%
  group_by(indicator, lag) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")
  
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

ggplot(heatmap_data, aes(x = lag, y = indicator, fill = mean_corr)) +
  geom_tile() +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed", size = 0.6) +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Top 5 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")


# Plot ccf Results Roll
ccf_tbl_roll %>%
  filter(industry_code %in% top05_pred,
         difference==0) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = " Top 5 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")

# Plot Distribution by Question
dcor_tbl_roll_peak %>% 
  filter(industry_code %in% top05_pred, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = " Top 5 - Development of Peak Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```


**Best early predictor (-6:-4)**

```{r Score Early Predictiors}
peak_dcor <- dcor_tbl_roll_peak %>%
  filter(level > 0,
         difference==0) %>%
  group_by(indicator, date_window_end) %>%
  slice_max(corr, n = 1, with_ties = FALSE) %>%
  select(indicator, date_window_end, corr) %>%
  rename(peak_corr = corr)

res_dcor <- dcor_tbl_roll %>%
  filter(level > 0,
         difference==0,
         lag %in% c(-6:-4)) %>%
  group_by(indicator, date_window_end, industry_code, level, sector) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  left_join(peak_dcor, by = join_by(indicator, date_window_end)) %>%
  mutate(res_corr = (peak_corr-mean_corr)^2)

score_tbl_roll <- res_dcor %>%
  group_by(industry_code, level, sector) %>%
  summarise(score = 1-mean(res_corr),
            var = var(res_corr),
            .groups = "drop") %>%
  arrange(desc(score))

score_tbl_roll %>% 
  ggplot(aes(x = sector, y = score)) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = "Score by Peak Correlation",
    x = "Sector",
    y = "Score"
  )

score_tbl_roll %>% 
  ggplot(aes(x = sector, y = var)) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Variance of Score by Peak Correlation",
    x = "Sector",
    y = "Variance"
  )

score_tbl_roll %>% 
  ggplot(aes(x = factor(level), y = score)) +
  geom_boxplot(outlier.size = 1, outlier.colour = "red") +
  theme_minimal() +
  labs(
    title = "Score by Peak Correlation",
    x = "Sector",
    y = "Variance"
  )

```

```{r Plot Early Predictors}
# Top Industries
top05_pred_early <- score_tbl_roll %>%
  filter(level %in% c(2)) %>%
  slice_max(score, n=5, with_ties = FALSE) %>%
  pull(industry_code)

top25_pred_early <- score_tbl_roll %>%
  filter(level %in% c(2)) %>%
  slice_max(score, n=25, with_ties = FALSE) %>%
  pull(industry_code)

#Plot CCF Full Window
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% top05_pred_early,
         difference==0) %>%
  group_by(indicator, lag) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop")
  
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(mean_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

ggplot(heatmap_data, aes(x = lag, y = indicator, fill = mean_corr)) +
  geom_tile() +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed", size = 0.6) +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Top 5 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")


# Plot ccf Results Roll
ccf_tbl_roll %>%
  filter(industry_code %in% top05_pred_early,
         difference==0) %>%
  group_by(indicator, lag, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(y = lag, x = date_window_end, fill = mean_corr)) +
  geom_tile() +
  facet_wrap(~indicator) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = " Top 5 - Avg. Cross-Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Mean Corr")

# Plot Distribution by Question
dcor_tbl_roll_peak %>% 
  filter(industry_code %in% top05_pred_early, 
         difference == 0,
         lag %in% c(-6:6)) %>%
  group_by(indicator, industry_code, date_window_end) %>%
  summarise(mean_corr = mean(corr, na.rm = TRUE), .groups = "drop") %>%
  group_by(indicator, date_window_end) %>%
  summarise(median_corr = median(mean_corr),
            q10 = quantile(mean_corr, 0.10),
            q25 = quantile(mean_corr, 0.25),
            q75 = quantile(mean_corr, 0.75),
            q90 = quantile(mean_corr, 0.90),
            .groups =  "drop") %>%
  ggplot(aes(x = date_window_end)) +
  facet_wrap(~ indicator) +
  geom_ribbon(aes(ymin = q10, ymax = q90), fill = "grey90") +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "grey60") +
  geom_line(aes(y = median_corr), color = "red") +
  scale_y_continuous(limits = c(0, 1)) +
  theme_minimal() +
  labs(
    title = " Top 5 - Development of Peak Correlation distribution by Question",
    x = "Date Window End",
    y = "Distance Correlation"
  )
```



## Prediction Models

### Setup

```{r ifo Data Import}
# Load Data
ifo_tsbl <- read_ifo_data() %>%
  preprocess_ifo_data() %>%
  mutate(date = yearmonth(date)) %>%      # Maybe push to read_ifo_data()
  as_tsibble(key = industry_code, index = date)

# Get Target Values as tsibble
target <- ifo_tsbl %>%
  filter(industry_code == "C0000000") %>%
  pivot_wider(
    id_cols = date,
    names_from = industry_code,
    values_from = KLD
  )
```


### Benchmark Models Predictions

**Setup**

```{r}
predictor <- ifo_tsbl %>%
  filter(level %in% c(2)) %>%
  select(-level) %>%
  pivot_wider(
    id_cols = date,
    names_from = industry_code,
    values_from = KLD
  ) %>% 
  left_join(target, by = "date") 
  

# Get Predictor Values
predictor_lag <- predictor %>%
  mutate(across(where(is.numeric), list(
    lag1 = ~lag(.x, 1),
    lag2 = ~lag(.x, 2),
    lag3 = ~lag(.x, 3),
    lag4 = ~lag(.x, 4),
    lag5 = ~lag(.x, 5),
    lag6 = ~lag(.x, 6)
  ), .names = "{.col}_{.fn}")) %>%
  select(contains("lag"))


# Drop NA Values
data <- predictor_lag %>%
  left_join(target, by = "date") %>%
  drop_na()

results <- data %>% 
  select(C0000000, date) %>%
  rename(main_index = C0000000)
```


**Predictions L1**

```{r}
y <- data$C0000000

X <- data %>%
  as_tibble() %>%
  select(-contains("C0000000"), -date) %>%
  as.matrix()

fit_net <- glmnet(X, y,
                  standardize = FALSE,
                  intercept = FALSE,
                  alpha = 0.8)
print(fit_net)
plot(fit_net)
plot(fit_net, xvar = "dev")

coefs_net <- coef(fit_net, s = 180)
coef_net <- rownames(coefs_net)[which(coefs_net != 0)] %>%
  str_sub(1,8)
coef_net
```

```{r}
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% coef_net) %>%
  summarise(median_corr = median(corr, na.rm = TRUE), 
            .by = c(lag, indicator))

# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(median_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot ccf Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(x = lag, y = indicator, fill = median_corr)) +
  geom_tile() +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed", size = 0.6) +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Median Cross Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Median Corr")
```

```{r}
y <- data$C0000000

X <- data %>%
  as_tibble() %>%
  select(contains(c(coef_net, "C0000000_lag"))) %>%
  as.matrix()

fit_lm <- lm(y ~ X)

summary.lm(fit_lm)

results <- results %>% 
  mutate(fitted_l1 = fitted(fit_lm))
```


**Predictions Corr**

```{r}
y <- data$C0000000

X <- data %>%
  as_tibble() %>%
  select(contains(c(top05_pred, "C0000000_lag"))) %>%
  as.matrix()

fit_lm <- lm(y ~ X)

summary.lm(fit_lm)

results <- results %>%
  mutate(fitted_score = fitted(fit_lm))
```


**Benchmark**

```{r}
y <- data$C0000000

X <- data %>%
  as_tibble() %>%
  select(contains("C0000000_lag")) %>%
  as.matrix()

fit_lm <- lm(y ~ X)

summary.lm(fit_lm)

results <- results %>%
  mutate(fitted_benchmark = fitted(fit_lm))
```


**Results**

```{r}
mse <- results %>%
  mutate(se_score = (main_index - fitted_score)^2,
         se_l1 = (main_index - fitted_l1)^2,
         se_benchmark = (main_index - fitted_benchmark)^2) %>%
  as_tibble() %>%
  summarise(mse_score = mean(se_score, na.rm = TRUE),
            mse_l1 = mean(se_l1, na.rm = TRUE),
            mse_benchmark = mean(se_benchmark, na.rm = TRUE),
            rmse_score = sqrt(mean(se_score, na.rm = TRUE)),
            rmse_l1  = sqrt(mean(se_l1,  na.rm = TRUE)),
            rmse_benchmark  = sqrt(mean(se_benchmark,  na.rm = TRUE)),
            .groups = "drop") %>%
  pivot_longer(
    everything(),
    names_to = c("metric", "model"),
    names_sep = "_",
    values_to = "value"
  ) %>%
  pivot_wider(
    names_from = metric,
    values_from = value
  )

print(mse)

cols <- c("main_index" = "blue", "fitted_l1" = "#F8766D", "fitted_score" = "#00BFC4")

results %>%
   pivot_longer(
    cols = c(main_index, fitted_l1, fitted_score),
    names_to = "variable",
    values_to = "value"
  ) %>%
  ggplot(aes(x = date, y = value, color = variable, alpha = variable)) +
  geom_line() +
  scale_alpha_manual(
    values = c("main_index" = 0.75, "fitted_l1" = 1, "fitted_score" = 1),  
    guide = "none"  # don’t show alpha in legend
  ) +
  scale_color_manual(
    values = cols,
    breaks = c("main_index", "fitted_l1", "fitted_score"),
    labels = c("Main Index", "ElasticNet", "Score Model")
  ) +
 
  theme_minimal() +
  labs(
    title = "Model Performance Early Predictions",
    x = "Date Window End",
    y = "KLD",
    color = "Model"
  )
```


### Benchmark Models Early Predictions

**Setup**

```{r}
predictor <- ifo_tsbl %>%
  filter(level %in% c(2)) %>%
  select(-level) %>%
  pivot_wider(
    id_cols = date,
    names_from = industry_code,
    values_from = KLD
  ) %>% 
  left_join(target, by = "date") 
  

# Get Predictor Values
predictor_lag <- predictor %>%
  mutate(across(where(is.numeric), list(
    lag4 = ~lag(.x, 4),
    lag5 = ~lag(.x, 5),
    lag6 = ~lag(.x, 6)
  ), .names = "{.col}_{.fn}")) %>%
  select(contains("lag"))


# Drop NA Values
data <- predictor_lag %>%
  left_join(target, by = "date") %>%
  drop_na()

results <- data %>% 
  select(C0000000, date) %>%
  rename(main_index = C0000000)
```


**Predictions L1**

```{r}
y <- data$C0000000

X <- data %>%
  as_tibble() %>%
  select(-contains("C0000000"), -date) %>%
  as.matrix()

fit_net <- glmnet(X, y,
                  standardize = FALSE,
                  intercept = FALSE,
                  alpha = 0.8)
print(fit_net)
plot(fit_net)
plot(fit_net, xvar = "dev")

coefs_net <- coef(fit_net, s = 180)
coef_net <- rownames(coefs_net)[which(coefs_net != 0)] %>%
  str_sub(1,8)
coef_net
```

```{r}
heatmap_data <- ccf_tbl_full %>%
  filter(industry_code %in% coef_net) %>%
  summarise(median_corr = median(corr, na.rm = TRUE), 
            .by = c(lag, indicator))

# Identify max correlation per indicator
highlight_points <- heatmap_data %>%
  group_by(indicator) %>%
  slice_max(abs(median_corr), n = 1, with_ties = FALSE) %>%  # absolute value now
  ungroup()

# Plot ccf Results with yellow borders on peak correlation
ggplot(heatmap_data, aes(x = lag, y = indicator, fill = median_corr)) +
  geom_tile() +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed", size = 0.6) +
  geom_tile(data = highlight_points,
            color = "yellow", size = 1.2, fill = NA) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0,
                       limits = c(-1, 1)) +
  theme_minimal() +
  labs(title = "Median Cross Correlation per Lag and Indicator (Peak highlighted)",
       x = "Lag",
       y = "Indicator",
       fill = "Median Corr")
```

```{r}
y <- data$C0000000

X <- data %>%
  as_tibble() %>%
  select(contains(c(coef_net, "C0000000_lag"))) %>%
  as.matrix()

fit_lm <- lm(y ~ X, intercept = FALSE)

summary.lm(fit_lm)

results <- results %>% 
  mutate(fitted_l1 = fitted(fit_lm))
```


**Predictions Corr**

```{r}
y <- data$C0000000

X <- data %>%
  as_tibble() %>%
  select(contains(c(top05_pred_early, "C0000000_lag"))) %>%
  as.matrix()

fit_lm <- lm(y ~ X)

summary.lm(fit_lm)

results <- results %>%
  mutate(fitted_score = fitted(fit_lm))
```


**Benchmark**

```{r}
y <- data$C0000000

X <- data %>%
  as_tibble() %>%
  select(contains("C0000000_lag")) %>%
  as.matrix()

fit_lm <- lm(y ~ X)

summary.lm(fit_lm)

results <- results %>%
  mutate(fitted_benchmark = fitted(fit_lm))
```


**Results**

```{r}
mse <- results %>%
  mutate(se_score = (main_index - fitted_score)^2,
         se_l1 = (main_index - fitted_l1)^2,
         se_benchmark = (main_index - fitted_benchmark)^2) %>%
  as_tibble() %>%
  summarise(mse_score = mean(se_score, na.rm = TRUE),
            mse_l1 = mean(se_l1, na.rm = TRUE),
            mse_benchmark = mean(se_benchmark, na.rm = TRUE),
            rmse_score = sqrt(mean(se_score, na.rm = TRUE)),
            rmse_l1  = sqrt(mean(se_l1,  na.rm = TRUE)),
            rmse_benchmark  = sqrt(mean(se_benchmark,  na.rm = TRUE)),
            .groups = "drop") %>%
  pivot_longer(
    everything(),
    names_to = c("metric", "model"),
    names_sep = "_",
    values_to = "value"
  ) %>%
  pivot_wider(
    names_from = metric,
    values_from = value
  )

print(mse)

cols <- c("main_index" = "blue", "fitted_l1" = "#F8766D", "fitted_score" = "#00BFC4")

results %>%
   pivot_longer(
    cols = c(main_index, fitted_l1, fitted_score),
    names_to = "variable",
    values_to = "value"
  ) %>%
  ggplot(aes(x = date, y = value, color = variable, alpha = variable)) +
  geom_line() +
  scale_alpha_manual(
    values = c("main_index" = 0.75, "fitted_l1" = 1, "fitted_score" = 1),  
    guide = "none"  # don’t show alpha in legend
  ) +
  scale_color_manual(
    values = cols,
    breaks = c("main_index", "fitted_l1", "fitted_score"),
    labels = c("Main Index", "ElasticNet", "Score Model")
  ) +
 
  theme_minimal() +
  labs(
    title = "Model Performance Early Predictions",
    x = "Date Window End",
    y = "KLD",
    color = "Model"
  )
```


