---
title: "Two-digit aggregates exploration"
output: html_notebook
---

Notebook for some basic exploration of all two-digit aggregates for business situation and expectation response, to get a feeling for their behaviour. 

```{r}
library(here) # great library to locate project root 

# source functions 
source(here("load_data.R"))
source(here("summary_tools.R"))
source(here("visualization.R"))

# load data and 'dictionaries' for industry 
data_path <- here("Data")
ifo_tbl <- read_ifo_data(data_path)

data_path_industries_dict <- here("Data_Dictionaries","industries_codes_titles.csv")
data_path_questions_dict <- here("Data_Dictionaries","questions_codes_titles.csv")

industry_df <- read.csv(data_path_industries_dict)
question_df <- read.csv(data_path_questions_dict)

# preprocess
ifo_tbl <- preprocess_ifo_data(ifo_tbl)
```


```{r}
# vector with industry code of all two-digit aggregats (excl. tobacco and pharma, due to NaN)
two_digit_aggregates <- c("C1000000", "C1100000", "C1300000", "C1400000", "C1500000", "C1600000", "C1700000", 
                          "C1800000", "C1900000", "C2000000", "C2100000", "C2200000", "C2300000", "C2400000",
                          "C2500000", "C2600000", "C2700000", "C2800000", "C2900000", "C3000000", "C3100000", "C3200000")
```

Univariate summaries for business situation. 

```{r}
univariate_summaries(ifo_tbl,
                     two_digit_aggregates,
                     question_codes = "GUS",
                     industry_dict = industry_df,
                     questions_dict = question_df)
```

Univariate summaries for business expectation

```{r}
univariate_summaries(ifo_tbl,
                     two_digit_aggregates,
                     question_codes = "GES",
                     industry_dict = industry_df,
                     questions_dict = question_df)

```

Have a look at the plots of these two questions, even though it will be quite messy obviously. 

```{r}
plot_industry_timeseries(ifo_tbl,
                         two_digit_aggregates,
                         "GUS",
                         industry_dict = industry_df,
                         questions_dict = question_df)

plot_industry_timeseries(ifo_tbl,
                         two_digit_aggregates,
                         "GES",
                         industry_dict = industry_df,
                         questions_dict = question_df)
```
Correlation structures across industries for current business situation:

```{r,fig.width=16, fig.height=10}
lag <- 0
corr_matrix <- lagged_corr_matrix(df = ifo_tbl,
                                 industry_codes = two_digit_aggregates,
                                 question_code = "GUS",
                                 lag = lag,
                                 industry_dict = industry_df)
plot_lagged_corr_heatmap(corr_matrix, lag = lag, wrap_width = 30)
```
Introducing a lag of three month, so seeing how much one industry at t - 6 (half a year earlier) is correlated with another industry at t. Lagged industries are shown in the rows

```{r,fig.width=16, fig.height=10}
lag <- 6
corr_matrix <- lagged_corr_matrix(df = ifo_tbl,
                                 industry_codes = two_digit_aggregates,
                                 question_code = "GUS",
                                 lag = lag,
                                 industry_dict = industry_df)
plot_lagged_corr_heatmap(corr_matrix, lag = lag, wrap_width = 30)
```
```{r,fig.width=16, fig.height=10}
lag <- 0
corr_matrix <- lagged_corr_matrix(df = ifo_tbl,
                                 industry_codes = two_digit_aggregates,
                                 question_code = "GES",
                                 lag = lag,
                                 industry_dict = industry_df)
plot_lagged_corr_heatmap(corr_matrix, lag = lag, wrap_width = 30)
```




```{r,fig.width=16, fig.height=10}
lag <- 6
corr_matrix <- lagged_corr_matrix(df = ifo_tbl,
                                 industry_codes = two_digit_aggregates,
                                 question_code = "GES",
                                 lag = lag,
                                 industry_dict = industry_df)
plot_lagged_corr_heatmap(corr_matrix, lag = lag, wrap_width = 30)
```